\documentclass{article}
\usepackage{titling, fullpage, setspace}

\title{Cover Letter for Peralta Colleges Application}
\date{}
\author{Efrem Rensi}

\begin{document}
\doublespacing
\maketitle
This is the cover letter accompanying my application for an adjunct teaching position in the Peralta College district.

I received my M.S. in Applied Mathematics from UC Davis in June 2014.  I was in a PhD program and opted for the masters after 7 years.  Immediately afterwards I was offered a job teaching at Woodland Community College (near Davis). I almost took it, but I was convinced otherwise by my parents who insisted that I could do better getting a high-paying tech job in the Bay Area.  I moved home to Oakland in Fall of 2015, where I currently live.   The idea was that I was going to focus my energy on developing my skills as a software engineer or data scientist, and get a tech job making a lot of money.

Fast forward to a year and a half later -- I have definitely developed my programming skills, worked on software projects, done volunteer work for a food distribution program, gotten in excellent shape hiking and running on regional park trails, and made a few friends, but still I don't have a job.  Part of preparing for software engineer jobs is solving algorithm design problems on a whiteboard. A few months ago I got a whiteboard and did a lot of Google interview problems on it.  It reminded me of my time as a TA.  Looking back on my years as a grad student, I fondly recall my teaching experiences.

I worked as a Teaching Assistant in graduate school for 7 years. I have been told that I was a good TA by several former students, and I enjoyed the teaching that I did.  I enjoyed the performance aspect of it, being a leader and facilitator, the problem solving, and I enjoyed helping people.  My father was also a math teacher at the university level, and later at Oakland High School until he retired.  After exploring other options I have renewed respect for my own apparent teaching talent, and I'd like to give it a shot as a career option.  I should add that I attended Laney college in the late 90s and 2001-2002.  I remember taking math classes at Laney, which got me on the path that led me here.

My PhD research was in computational linear algebra.  I enjoy algebra and linear algebra, and I think I could teach those courses well.  I always liked discrete math and I'd love to teach that.  I was told there is a demand for statistics teachers; I have little experience with Statistics but given time to catch up, I'm pretty sure I could teach that too.  If you are looking for teachers who can adopt new technology, I'm up for that.   I once was a TA for a class with a large online component.  I held video-chat office hours and particpated in the course chatroom.  I have a lot of experience with Matlab and Python programming.  I TA'd an introduction to Matlab course that was motivated by linear algrbra concepts.   I could probably teach a computer programming class.
I'm interested in teaching part-time: 1 or 2 classes.  I would also consider grading if people are ever hired exclusively as readers, but I prefer being an instructor.  And, lastly, I would consider a tutoring postion.  I live in Oakland and I am willing to work at any Peralta campus.   Thank you!
\end{document}
